%====================
% EXPERIENCE 0
%====================
\subsection{{independent projects }}

\begin{zitemize}
             \item{ 
             AMN MOJ E-commerce company: Gomrok Web application.}
             \item{
                Implemented Azad fekri social media PWA (twitter like app about future of Iran's politics and freedom)}
             \item{
                participate in a VOD - VR project, showing live event with the capability of 3d view and camera selecting. mobile version used Gyroscope and desktop version used mouse motion to detect the motion and change the 360 view using Videojs .
                }


\end{zitemize}
%====================
% EXPERIENCE A
%====================
\subsection{{Front-End Developer \hfill April 2022 - Present}}
\subtext{Pixaldo (Remote) \hfill Germany \\One of the major German companies in the field of warehousing and logistics organizes the warehouse as well as the dispatch. implement user-friendly, world-class react mobile application(PWA) for medium-sized warehouse management for business owners. }
\begin{zitemize}
             \item{
                Participate in code review, and interview process, responsible for onboarding new teammates.}
             \item{
                Develop various wizard flows for complex data collection and validation and architecture of submitted data using Redux (e.g. develop wizards for multiple warehouses with more than 10,000 items and 100 corridors)}
             \item{
                Followed ES6/TypeScript clean code best practices within an Agile environment to produce rapid iterations for more than 20 major companies as our clients. (file architecture and optimized data store)}

\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{Front-End Developer \hfill January 2022 - October 2022}}
\subtext{Freelance (Remote) \hfill United States\\ Server and uptime monitoring web application startup located in silicon valley.}
\begin{zitemize}

             \item{
                Migrated UI from the old Angular version to React and keep its page size below 300kB.}
             \item{
                Implemented for supporting real-time monitoring of 30+ servers per page using Web Socket (Socket.IO).}
             \item{
               Implemented a JavaScript Linux CLI comamand builder based on user input and back-end data.}

             \item{
               Managed tight deadlines in an agile environment, Cross-cultural teamwork, and negotiation of UX enhancements.
}
\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{{WordPress Developer (theme and UI)\hfill June 2020 - June 2022}}
\subtext{Calistu (Hybrid)\hfill United Arab Emirates \\ Digital marketing startup based in Dubai participated in a major wide range of business IT collaborations.}
\begin{zitemize}

             \item{
                Developed More than 40 WordPress websites and 3 headless projects for 5 countries and 3+ languages.}
             \item{Implemented complex client-side rendering UI logic with the Case use of React with CDN in the WordPress building blocks.}
             \item{
                Implemented an automatic system for the update, backup, and security warning for 40+ projects.}

\end{zitemize}


%====================
% EXPERIENCE E
%====================
%\subsection{{ROLE / PROJECT E \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company E \hfill somewhere, state}
%\begin{zitemize}
%\item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%\item Ut malesuada purus at mi placerat dapibus.
%\item Suspendisse finibus massa eu nisi dictum, a imperdiet tellus convallis.
%\item Nam feugiat erat vestibulum lacus feugiat, efficitur gravida nunc imperdiet.
%\item Morbi porta lacus vitae augue luctus, a rhoncus est sagittis.
%\end{zitemize}
